A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

% this is explained at https://github.com/tectonic-typesetting/tectonic/issues/70#issuecomment-974462614
\PassOptionsToClass{pdflatex}{sn-jnl}
\documentclass[sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals

\usepackage{graphicx}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{xcolor}%
\usepackage{manyfoot}%

@@

@@

\begin{figure}
\begin{centering}
\includegraphics[width=\textwidth]{figures/all_phot_nature_delta_flux.pdf}
%\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_simple.pdf}
\caption{Optical and infrared photometry of ASASSN-21qj.
%
Panel {\bf a} is normalised optical photometry from ASAS-SN in $V$-band and $g'$ band.
%
Panel {\bf b} shows the fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, where a value of 1.0 represents the stellar contribution alone.
%
Panel {\bf c} shows the calculated $NEOWISE$ color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no IR excess, and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\label{fig:wisephot}
\script{plot_all_phot_nature_delta_flux.py}
%\script{plot_master_lightcurve_nature_simple.py}
\end{centering}
\end{figure}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_simple.pdf}
      \caption{The light curve of ASASSN-21qj from several different photometric surveys and the derived transverse velocities.
      %
      Panel {\bf a} shows that the eclipse depth is deeper for shorter wavelengths, indicating that the transiting material is dominated by sub-micron sized grains.
      %
      Panel {\bf b} shows the  transverse velocities derived from the light curve gradients.
      %
      These are lower limits to the true velocity, and thus imply that the transiting material is closer to the star than 16\,au.
      %
      Error bars are shown at $1\sigma$ confidence.
      }
        \label{fig:eclipse_overview}
\script{plot_master_lightcurve_nature_simple.py}
\end{centering}
\end{figure*}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=\columnwidth]{figures/Size_cooling_combined_figure.pdf}
\caption{The size and temporal evolution of a post-impact body.
%
A post-impact body of a few to tens of Earth masses could be large enough to explain the observed increase in thermal emission from ASASSN-21qj and the subsequent infrared fluxes.
%
Panel {\bf a} shows the Hill radii for bodies at different semi-major axis (solid colored lines) and the Bondi radii (dotted lines) assuming different compositions for the vapor of the post-impact body.
%
The horizontal black dashed line shows the radii required to explain the observed flux at the inferred emission temperature of 1000~K. 
%
The change in excess flux due to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles is in panel {\bf b}, eqn~\ref{eqn:sigma} and for different mass bodies in panel {\bf c}.
%
Each example had an initial radius of 7\,$R_\odot$, a radiative temperature of 1000~K, and a corresponding initial flux of 0.04\,$L_\star$, as estimated for the observed infrared emittor.
%
The solid lines are profiles that can have non-zero initial density at the initial emitting radius, and the dashed lines are for ones that are forced to have zero density at the initial emitting radius.
%
When not stated, the mass of the post-impact body was 50~$M_{\rm Earth}$, the power law exponent is $-2$, and the size of the central region was 10~$R_{\rm Earth}$.
}
\label{fig:Hill_Bondi_R}
\script{plot_hill_bondi_radii_three_panels.py}

@@

@@

@@

% \begin{thebibliography}{10}
% \expandafter\ifx\csname url\endcsname\relax
%   \def\url#1{\burl{#1}}\fi
% \expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
% \providecommand{\bibinfo}[2]{#2}
% \providecommand{\eprint}[2][]{\url{#2}}
% \providecommand{\doi}[1]{\url{https://doi.org/#1}}
% \bibcommenthead

% \bibitem{Williams11}
% \bibinfo{author}{{Williams}, J.~P.} \& \bibinfo{author}{{Cieza}, L.~A.}
% \newblock \bibinfo{title}{{Protoplanetary Disks and Their Evolution}}.
% \newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{49}},
%   \bibinfo{pages}{67--117} (\bibinfo{year}{2011}).
% \newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2011ARA%26A..49...67W}.

% \bibitem{Wyatt15}
% \bibinfo{author}{{Wyatt}, M.~C.}, \bibinfo{author}{{Pani{\'c}}, O.},
%   \bibinfo{author}{{Kennedy}, G.~M.} \& \bibinfo{author}{{Matr{\`a}}, L.}
% \newblock \bibinfo{title}{{Five steps in the evolution from protoplanetary to
%   debris disk}}.
% \newblock \emph{\bibinfo{journal}{\apss}} \textbf{\bibinfo{volume}{357}},
%   \bibinfo{pages}{103} (\bibinfo{year}{2015}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2015Ap&SS.357..103W}.

% \bibitem{Hughes18}
% \bibinfo{author}{{Hughes}, A.~M.}, \bibinfo{author}{{Duch{\^e}ne}, G.} \&
%   \bibinfo{author}{{Matthews}, B.~C.}
% \newblock \bibinfo{title}{{Debris Disks: Structure, Composition, and
%   Variability}}.
% \newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{56}},
%   \bibinfo{pages}{541--591} (\bibinfo{year}{2018}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018ARA&A..56..541H}.

% \bibitem{2014Sci...345.1032M}
% \bibinfo{author}{{Meng}, H. Y.~A.} \emph{et~al.}
% \newblock \bibinfo{title}{{Large impacts around a solar-analog star in the era
%   of terrestrial planet formation}}.
% \newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{345}},
%   \bibinfo{pages}{1032--1035} (\bibinfo{year}{2014}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2014Sci...345.1032M}.

% \bibitem{Su19}
% \bibinfo{author}{{Su}, K. Y.~L.} \emph{et~al.}
% \newblock \bibinfo{title}{{Extreme Debris Disk Variability: Exploring the
%   Diverse Outcomes of Large Asteroid Impacts During the Era of Terrestrial
%   Planet Formation}}.
% \newblock \emph{\bibinfo{journal}{\aj}} \textbf{\bibinfo{volume}{157}},
%   \bibinfo{pages}{202} (\bibinfo{year}{2019}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2019AJ....157..202S}.

% \bibitem{Su22}
% \bibinfo{author}{{Su}, K. Y.~L.}, \bibinfo{author}{{Kennedy}, G.~M.},
%   \bibinfo{author}{{Schlawin}, E.}, \bibinfo{author}{{Jackson}, A.~P.} \&
%   \bibinfo{author}{{Rieke}, G.~H.}
% \newblock \bibinfo{title}{{A Star-sized Impact-produced Dust Clump in the
%   Terrestrial Zone of the HD 166191 System}}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{927}},
%   \bibinfo{pages}{135} (\bibinfo{year}{2022}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ApJ...927..135S}.

% \bibitem{2021ApJ...918...71R}
% \bibinfo{author}{{Rieke}, G.~H.}, \bibinfo{author}{{Su}, K.~Y.~L.},
%   \bibinfo{author}{{Melis}, C.} \& \bibinfo{author}{{G{\'a}sp{\'a}r}, A.}
% \newblock \bibinfo{title}{{Extreme Variability of the V488 Persei Debris
%   Disk}}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{918}},
%   \bibinfo{pages}{71} (\bibinfo{year}{2021}).

% \bibitem{RizzoSmith21}
% \bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
% \newblock \bibinfo{title}{{ASASSN-21qj: A Rapidly Fading, Sun-Like Star}}.
% \newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
%   \textbf{\bibinfo{volume}{14879}}, \bibinfo{pages}{1} (\bibinfo{year}{2021}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2021ATel14879....1R}.

% \bibitem{RizzoSmith22}
% \bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
% \newblock \bibinfo{title}{{An Update on ASASSN-21qj: A Rapidly Fading, Sun-Like
%   Star; Back With a Vengeance}}.
% \newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
%   \textbf{\bibinfo{volume}{15531}}, \bibinfo{pages}{1} (\bibinfo{year}{2022}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ATel15531....1R}.

% \bibitem{shappee_man_2014}
% \bibinfo{author}{Shappee, B.~J.} \emph{et~al.}
% \newblock \bibinfo{title}{The {Man} behind the {Curtain}: {X}-{Rays} {Drive}
%   the {UV} through {NIR} {Variability} in the 2013 {Active} {Galactic}
%   {Nucleus} {Outburst} in {NGC} 2617}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{788}},
%   \bibinfo{pages}{48} (\bibinfo{year}{2014}).
% \newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2014ApJ...788...48S}.

% \bibitem{kochanek_all-sky_2017}
% \bibinfo{author}{Kochanek, C.~S.} \emph{et~al.}
% \newblock \bibinfo{title}{The {All}-{Sky} {Automated} {Survey} for {Supernovae}
%   ({ASAS}-{SN}) {Light} {Curve} {Server} v1.0}.
% \newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
%   the Pacific}} \textbf{\bibinfo{volume}{129}}, \bibinfo{pages}{104502}
%   (\bibinfo{year}{2017}).
% \newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2017PASP..129j4502K}.

% \bibitem{Lock2017}
% \bibinfo{author}{Lock, S.~J.} \& \bibinfo{author}{Stewart, S.~T.}
% \newblock \bibinfo{title}{The structure of terrestrial bodies: {Impact}
%   heating, corotation limits, and synestias}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
%   \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{950--982}
%   (\bibinfo{year}{2017}).
% \newblock \urlprefix\url{http://doi.wiley.com/10.1002/2016JE005239}.

% \bibitem{2009ApJ...704..770M}
% \bibinfo{author}{{Miller-Ricci}, E.}, \bibinfo{author}{{Meyer}, M.~R.},
%   \bibinfo{author}{{Seager}, S.} \& \bibinfo{author}{{Elkins-Tanton}, L.}
% \newblock \bibinfo{title}{{On the Emergent Spectra of Hot Protoplanet Collision
%   Afterglows}}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{704}},
%   \bibinfo{pages}{770--780} (\bibinfo{year}{2009}).

% \bibitem{Schlichting2018a}
% \bibinfo{author}{Schlichting, H.~E.}
% \newblock \bibinfo{title}{ in \textit{Formation of super-{Earths}}} (eds
%   \bibinfo{editor}{Hans, D.} \& \bibinfo{editor}{Belmonte, J.~A.})
%   \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}}
%   (\bibinfo{publisher}{Springer}, \bibinfo{year}{2018}).
% \newblock \urlprefix\url{http://arxiv.org/abs/1802.03090}.
% \newblock \bibinfo{note}{ArXiv: 1802.03090}.

% \bibitem{DAngelo2018}
% \bibinfo{author}{D’Angelo, G.} \& \bibinfo{author}{Lissauer, J.~J.}
% \newblock \bibinfo{title}{ in \textit{Formation of {Giant} {Planets}}} (eds
%   \bibinfo{editor}{Deeg, H.~J.} \& \bibinfo{editor}{Belmonte, J.~A.})
%   \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}} \bibinfo{pages}{1--25}
%   (\bibinfo{publisher}{Springer International Publishing},
%   \bibinfo{address}{Cham}, \bibinfo{year}{2018}).
% \newblock \urlprefix\url{https://doi.org/10.1007/978-3-319-30648-3_140-2}.

% \bibitem{Kaib2016}
% \bibinfo{author}{Kaib, N.~A.} \& \bibinfo{author}{Chambers, J.~E.}
% \newblock \bibinfo{title}{The fragility of the terrestrial planets during a
%   giant-planet instability}.
% \newblock \emph{\bibinfo{journal}{\mnras}} \textbf{\bibinfo{volume}{455}},
%   \bibinfo{pages}{3561--3569} (\bibinfo{year}{2016}).
% \newblock \urlprefix\url{https://doi.org/10.1093/mnras/stv2554}.

% \bibitem{Nakajima2015}
% \bibinfo{author}{Nakajima, M.} \& \bibinfo{author}{Stevenson, D.~J.}
% \newblock \bibinfo{title}{Melting and mixing states of the {Earth}'s mantle
%   after the {Moon}-forming impact}.
% \newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
%   \textbf{\bibinfo{volume}{427}}, \bibinfo{pages}{286--295}
%   (\bibinfo{year}{2015}).
% \newblock
%   \urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0012821X15003805}.

% \bibitem{Carter2020}
% \bibinfo{author}{Carter, P.~J.}, \bibinfo{author}{Lock, S.~J.} \&
%   \bibinfo{author}{Stewart, S.~T.}
% \newblock \bibinfo{title}{The {Energy} {Budgets} of {Giant} {Impacts}}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
%   \textbf{\bibinfo{volume}{125}} (\bibinfo{year}{2020}).
% \newblock \bibinfo{note}{ArXiv: 1912.04936}.

% \bibitem{Canup2001}
% \bibinfo{author}{Canup, R.~M.} \& \bibinfo{author}{Asphaug, E.}
% \newblock \bibinfo{title}{Origin of the {Moon} in a giant impact near the end
%   of the {Earth}'s formation}.
% \newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{412}},
%   \bibinfo{pages}{708--12} (\bibinfo{year}{2001}).
% \newblock \urlprefix\url{http://dx.doi.org/10.1038/35089010}.

% \bibitem{Lock18}
% \bibinfo{author}{{Lock}, S.~J.} \emph{et~al.}
% \newblock \bibinfo{title}{{The Origin of the Moon Within a Terrestrial
%   Synestia}}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research (Planets)}}
%   \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{910--951}
%   (\bibinfo{year}{2018}).
% \newblock
%   \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018JGRE..123..910L}.

% \bibitem{Benz2008_Mercury_book}
% \bibinfo{author}{Benz, W.}, \bibinfo{author}{Anic, A.},
%   \bibinfo{author}{Horner, J.} \& \bibinfo{author}{Whitby, J.~A.}
% \newblock \bibinfo{title}{ in \textit{The {Origin} of {Mercury}}} (eds
%   \bibinfo{editor}{Balogh, A.}, \bibinfo{editor}{Ksanfomality, L.} \&
%   \bibinfo{editor}{von Steiger, R.}) \emph{\bibinfo{booktitle}{Mercury}} Space
%   {Sciences} {Series} of {ISSI}, \bibinfo{pages}{7--20}
%   (\bibinfo{publisher}{Springer}, \bibinfo{address}{New York, NY},
%   \bibinfo{year}{2008}).
% \newblock \urlprefix\url{https://doi.org/10.1007/978-0-387-77539-5_2}.

% \bibitem{Leinhardt2015}
% \bibinfo{author}{Leinhardt, Z.~M.}, \bibinfo{author}{Dobinson, J.},
%   \bibinfo{author}{Carter, P.~J.} \& \bibinfo{author}{Lines, S.}
% \newblock \bibinfo{title}{Numerically predicted indirect signatures of
%   terrestrial planet formation}.
% \newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{806}},
%   \bibinfo{pages}{23} (\bibinfo{year}{2015}).
% \newblock \urlprefix\url{https://doi.org/10.1088/0004-637X/806/1/23}.

% \bibitem{Carter2020a}
% \bibinfo{author}{Carter, P.~J.} \& \bibinfo{author}{Stewart, S.~T.}
% \newblock \bibinfo{title}{Colliding in the {Shadows} of {Giants}:
%   {Planetesimal} {Collisions} during the {Growth} and {Migration} of {Gas}
%   {Giants}}.
% \newblock \emph{\bibinfo{journal}{The Planetary Science Journal}}
%   \textbf{\bibinfo{volume}{1}}, \bibinfo{pages}{45} (\bibinfo{year}{2020}).
% \newblock \urlprefix\url{https://doi.org/10.3847/PSJ/abaecc}.
% \newblock \bibinfo{note}{ArXiv: 2008.05549 Publisher: IOP Publishing}.

% \bibitem{Stewart2008}
% \bibinfo{author}{Stewart, S.~T.}, \bibinfo{author}{Seifter, A.} \&
%   \bibinfo{author}{Obst, A.~W.}
% \newblock \bibinfo{title}{Shocked {H2O} ice: {Thermal} emission measurements
%   and the criteria for phase changes during impact events}.
% \newblock \emph{\bibinfo{journal}{Geophysical Research Letters}}
%   \textbf{\bibinfo{volume}{35}}, \bibinfo{pages}{L23203}
%   (\bibinfo{year}{2008}).
% \newblock \urlprefix\url{http://doi.wiley.com/10.1029/2008GL035947}.
% \newblock \bibinfo{note}{ISBN: 0094-8276}.

% \bibitem{Davies2020}
% \bibinfo{author}{Davies, E.~J.} \emph{et~al.}
% \newblock \bibinfo{title}{Silicate {Melting} and {Vaporization} {During}
%   {Rocky} {Planet} {Formation}}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
%   \textbf{\bibinfo{volume}{125}} (\bibinfo{year}{2020}).
% \newblock
%   \urlprefix\url{https://onlinelibrary.wiley.com/doi/abs/10.1029/2019JE006227}.
% \newblock \bibinfo{note}{ArXiv: 2002.00998 Publisher: John Wiley \& Sons, Ltd}.

% \bibitem{Johnson2015}
% \bibinfo{author}{Johnson, B.~C.}, \bibinfo{author}{Minton, D.~A.},
%   \bibinfo{author}{Melosh, H.~J.} \& \bibinfo{author}{Zuber, M.~T.}
% \newblock \bibinfo{title}{Impact jetting as the origin of chondrules}.
% \newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
%   \bibinfo{pages}{339--341} (\bibinfo{year}{2015}).
% \newblock \urlprefix\url{http://dx.doi.org/10.1038/nature14105}.
% \newblock \bibinfo{note}{Publisher: Nature Publishing Group, a division of
%   Macmillan Publishers Limited. All Rights Reserved.}

% \bibitem{Caracas2023}
% \bibinfo{author}{Caracas, R.} \& \bibinfo{author}{Stewart, S.~T.}
% \newblock \bibinfo{title}{No magma ocean surface after giant impacts between
%   rocky planets}.
% \newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
%   \textbf{\bibinfo{volume}{608}}, \bibinfo{pages}{118014}
%   (\bibinfo{year}{2023}).
% \newblock
%   \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0012821X23000274}.

% \bibitem{Fegley2023_BSE_cond}
% \bibinfo{author}{Fegley, B.}, \bibinfo{author}{Lodders, K.} \&
%   \bibinfo{author}{Jacobson, N.~S.}
% \newblock \bibinfo{title}{Chemical equilibrium calculations for bulk silicate
%   earth material at high temperatures}.
% \newblock \emph{\bibinfo{journal}{Geochemistry}} \bibinfo{pages}{125961}
%   (\bibinfo{year}{2023}).
% \newblock
%   \urlprefix\url{https://www.sciencedirect.com/science/article/pii/S0009281923000120}.

% \bibitem{Lock2018moon}
% \bibinfo{author}{Lock, S.~J.} \emph{et~al.}
% \newblock \bibinfo{title}{The origin of the {Moon} within a terrestrial
%   synestia}.
% \newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
%   \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{910--951}
%   (\bibinfo{year}{2018}).
% \newblock \urlprefix\url{http://doi.wiley.com/10.1002/2017JE005333}.
% \newblock \bibinfo{note}{ArXiv: 1802.10223v1}.

% \bibitem{Lock2020}
% \bibinfo{author}{Lock, S.~J.}, \bibinfo{author}{Stewart, S.~T.} \&
%   \bibinfo{author}{Ćuk, M.}
% \newblock \bibinfo{title}{The energy budget and figure of {Earth} during
%   recovery from the {Moon}-forming giant impact}.
% \newblock \emph{\bibinfo{journal}{Earth and Planetary Science Letters}}
%   \textbf{\bibinfo{volume}{530}}, \bibinfo{pages}{115885}
%   (\bibinfo{year}{2020}).
% \newblock \urlprefix\url{https://doi.org/10.1016/j.epsl.2019.115885}.
% \newblock \bibinfo{note}{ArXiv: 1910.00619 Publisher: Elsevier}.

% %%%%%%%%%%%
% %%% 30
% %%%%%%%%%%%%

% \end{thebibliography}

% \clearpage

@@

@@

The beginning of the eclipse was announced \cite{RizzoSmith21} by the ASAS-SN survey, which triggered several observing campaigns at optical wavelengths and an ALMA observation at Band 7 (program \texttt{2019.A.00040.S}).
%
The photometric data and passband filters are listed in Extended Data Table~\ref{tab:photometry}.

% ░█████╗░░██████╗░█████╗░░██████╗
% ██╔══██╗██╔════╝██╔══██╗██╔════╝
% ███████║╚█████╗░███████║╚█████╗░
% ██╔══██║░╚═══██╗██╔══██║░╚═══██╗
% ██║░░██║██████╔╝██║░░██║██████╔╝
% ╚═╝░░╚═╝╚═════╝░╚═╝░░╚═╝╚═════╝░

The All Sky Automated Survey \cite[ASAS; ][]{pojmanski_all_1997, asas_2005, asas_2018} is a survey consisting of two observing stations - one in Las Campanas, Chile and the other on Maui, Hawaii. 
%
Each observatory is equipped with two CCD cameras using V and I filters and commercial f $ = 200$ mm, D $= 100$ mm lenses, although both larger (D $=250$ mm) and smaller (50-72 mm) lenses were used at earlier times.
%
The majority of the data are taken with a pixel scale of $\approx$ 15\arcsec{}.
%
ASAS splits the sky into 709 partially overlapping 9\degr{} $\times$ 9\degr{} fields, taking on average 150 3-minute exposures per night, leading to a variable cadence of 0-2 frames per night.
%
Depending on the equipment used and the mode of operation, the ASAS limiting magnitude varied between 13.5 and 15.5 mag in V, and the saturation limit was 5.5 to 7.5 mag. 
%
Precision is around 0.01-0.02 mag for bright stars and below 0.3 mag for the fainter ones. 
%
ASAS photometry is calibrated against the Tycho catalog, and its accuracy is limited to 0.05 mag for bright, non-blended stars.

@@

@@

\subsubsection*{Dust properties from optical colors}

>>>>

% this is explained at https://github.com/tectonic-typesetting/tectonic/issues/70#issuecomment-974462614
\PassOptionsToClass{pdflatex}{sn-jnl}
\documentclass[sn-nature,oneside]{sn-jnl}% Style for submissions to Nature Portfolio journals
%%%NOTE: The documentclass has been edited

\usepackage{graphicx}%
\usepackage{amsmath,amssymb}%
\usepackage{xcolor}% % already required in cls
\usepackage{manyfoot}%

@@

%%==================================%%
%% sample for unstructured abstract %%
%%==================================%%

@@

\begin{figure}
\begin{centering}
\includegraphics[width=\textwidth]{figures/all_phot_nature_delta_flux.pdf}
%\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_simple.pdf}
\caption{\textbf{Optical and infrared photometry of ASASSN-21qj.}
%
{\bf a}, Normalized optical photometry from \gls{asassn} in the $V$-band and the $g'$ band.
%
{\bf b},Fractional flux increase in brightness of ASASSN-21qj in both the $W1$ and $W2$ bands, for which a value of 1.0 represents the stellar contribution alone.
%
{\bf c},Calculated NEOWISE color temperature estimated from the photometry of the two bands.
%
The color temperature is plotted as zero when there is no infrared excess and is consistent with a temperature of 1000\,K while the excess is present.
%
Error bars are shown at $1\sigma$ confidence.
}
\label{fig:wisephot}
\script{plot_all_phot_nature_delta_flux.py}
%\script{plot_master_lightcurve_nature_simple.py}
\end{centering}
\end{figure}

@@

@@

% 205 words

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.0\textwidth]{figures/master_lightcurve_nature_simple.pdf}
      \caption{\textbf{The light curve of ASASSN-21qj from several different photometric surveys and the derived transverse velocities.}
      %
      {\bf a},The eclipse depth is deeper for shorter wavelengths, indicating that the transiting material is dominated by sub-micron sized grains.
      %
      {\bf b},Transverse velocities derived from the light-curve gradients.
      %
      These are lower limits to the true velocity, and thus imply that the transiting material is closer to the star than 16\,au.
      %
      Error bars are shown at $1\sigma$ confidence.
      }
        \label{fig:eclipse_overview}
\script{plot_master_lightcurve_nature_simple.py}
\end{centering}
\end{figure*}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=\columnwidth]{figures/Size_cooling_combined_figure.pdf}
\caption{\textbf{The size and temporal evolution of a post-impact body.}
%
A post-impact body of a few to tens of Earth masses could be large enough to explain the observed increase in thermal emission from ASASSN-21qj and the subsequent infrared fluxes.
%
{\bf a},The Hill radii for bodies at different semi-major axes (solid colored lines) and the Bondi radii (dashed lines) assuming different compositions for the vapor of the post-impact body.
%
The horizontal black dashed line shows the radius required to explain the observed flux at the inferred emission temperature of 1000~K. 
%
{\bf b,c},The change in excess flux owing to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles ({\bf b}; equation~\ref{eqn:sigma}) and for different mass bodies ({\bf c}).
%
Each example had an initial radius of 7\,$R_\odot$, a radiative temperature of 1000~K, and a corresponding initial flux of 0.04\,$L_\star$, as estimated for the observed infrared emitter.
%
The solid lines are profiles that can have non-zero initial density at the initial emitting radius, and the dashed lines are for ones that are forced to have zero density at the initial emitting radius.
%
When not stated, the mass of the post-impact body was 50~$M_{\rm Earth}$, the power law exponent is $-2$, and the size of the central region was 10~$R_{\rm Earth}$.
}
\label{fig:Hill_Bondi_R}
\script{plot_hill_bondi_radii_three_panels.py}

@@

@@

\begin{figure}[h!]
    \centering
\includegraphics[width=0.8\textwidth]{figures/sed.pdf}
    \caption{\textbf{Spectrum of \asas{}~components.} The red symbols show the optical and pre-brightnening \gls{wise} infrared photometry and the blue symbols show the post-brightnening \gls{wise} and \gls{alma} fluxes. Stellar and 1000\,K components consistent with the pre- and post-brightening fluxes are shown. The dashed line shows an estimated cool component spectrum for \SI{0.1}{\micro\metre}-sized grains associated with the transiting dust cloud. Downward triangles are upper limits.
    %
    Error bars are shown at $1\sigma$ confidence.
}
    \label{fig:sed}
   \script{fvsr.py}
\end{figure}
%

\begin{table}
    \centering
    \caption{Properties of \asas}
    \begin{tabular}{@{}lc@{}}
    \hline\hline
Property                               & Value                    \\
        \hline
         $\alpha_{ICRS}$, {[}hh mm ss{]}  & 08:15:23.30\footnotemark[1]  \\
         $\delta_{ICRS}$, {[}dd mm ss{]}  & -38:59:23.3\footnotemark[1]  \\
         $\mu_{\alpha}$ {[}mas yr$^{-1}${]}     & $-9.692\pm0.012$\footnotemark[1]   \\
         $\mu_{\delta}$ {[}mas yr$^{-1}${]}     & $7.349\pm0.012$\footnotemark[1]  \\
         $\varpi$ {[}mas{]}                     & $1.763\pm0.011$\footnotemark[1]   \\
         RV {[}km s$^{-1}${]}                   & $25.8\pm3$\footnotemark[1] \\
         Distance {[}pc{]}                      & $567.2^{+6.7}_{-5.9}$\footnotemark[2] \\ 
        \hline
         $G$ {[}mag{]}                          & $13.371\pm 0.003$\footnotemark[1]  \\
         $G_{BP}$ {[}mag{]}                     & $13.697\pm 0.003$\footnotemark[1]    \\
         $G_{RP}$ {[}mag{]}                     & $12.882\pm 0.004$\footnotemark[1]   \\
         $G_{BP}-G_{RP}$ {[}mag{]}              & $0.815\pm 0.005$\footnotemark[1]         \\
         $J$ {[}mag{]}                          & $>12.07$\footnotemark[3]   \\
         $H$ {[}mag{]}                          & $12.03\pm0.04$\footnotemark[3]    \\
         $K_s$ {[}mag{]}                          & $11.99\pm0.04$\footnotemark[3]    \\
         $B$ (AB) {[}mag{]}                     & $14.16\pm0.06$\footnotemark[4]     \\
         $V$ (AB) {[}mag{]}                     & $13.48\pm0.03$\footnotemark[4]   \\
         $g'$ (AB) {[}mag{]}                     & $13.77\pm0.03$\footnotemark[4]  \\
         $r'$ (AB) {[}mag{]}                     & $13.29\pm0.03$\footnotemark[4]     \\
         $i'$ (AB) {[}mag{]}                     & $13.20\pm0.08$\footnotemark[4]   \\
        \hline
%         $M_*$ [$M_{\odot}$]                    & $0.85\pm0.02$  \\
         \teff{} [K]                            & $5760\pm10$\footnotemark[1]  \\
         {[}Fe/H{]} [dex]                       & $-0.23\pm0.01$\footnotemark[1] \\
         log\,$g$ [log$_{10}$ cm\,s$^{-2}$]     & $4.339\pm0.005$\footnotemark[1]  \\
         $R_*$ [\rsun{}]                        & $1.04$\footnotemark[5] \\
         log($L_{bol}/L_{\odot}$) [dex]         & $0.033$\footnotemark[5] \\
         $m_{bol}$ [mag]                        & $13.49\pm0.02$\footnotemark[6] \\
         $E(G_{BP}-G_{RP})$ {[}mag{]}           & $0.01 \pm 0.005$\footnotemark[6]    \\
         Age [Myr]                              & $300\pm92$\footnotemark[7] \\

@@

The beginning of the eclipse was announced \cite{RizzoSmith21} by the ASAS-SN survey, which triggered several observing campaigns at optical wavelengths and an ALMA observation at Band 7 (program \texttt{2019.A.00040.S}).
%

\begin{table}
    \centering
    \caption{Photometric observations of ASASSN-21qj. The number of points are listed per survey and filter. %
    %
    This is the count after initial rejection of photometric points with significantly large error bars.
    %
    Further photometric points may have been rejected in the differeny analysis steps.
    %
    The ROAD observations constitute the majority of observations from the AAVSO data sets.}
    \begin{tabular}{@{}lcc@{}}
    \hline\hline
Survey name  & Filter & Number of points                    \\
        \hline
ASASSN   &  $V$   & 758 \\
   &  $g'$   & 3225 \\
        \hline
ATLAS & $c$ & 161 \\
 & $o$ & 677 \\
        \hline
AAVSO   &  $B$   & 729 \\    % 601 in RVC
   &  $I$   & 728 \\    % 612 in RVC
   &  $V$   & 722 \\    % 599 in RVC
        \hline
LCOGT   &  $g$   & 275 \\    % RVC
   &  $r$   & 224 \\    % RVC
   &  $i$   & 168 \\    % RVC
        \hline
NEOWISE & $W1$ & 18 \\
 & $W2$ & 18 \\
        \hline
    \end{tabular}

% ░█████╗░░██████╗░█████╗░░██████╗
% ██╔══██╗██╔════╝██╔══██╗██╔════╝
% ███████║╚█████╗░███████║╚█████╗░
% ██╔══██║░╚═══██╗██╔══██║░╚═══██╗
% ██║░░██║██████╔╝██║░░██║██████╔╝
% ╚═╝░░╚═╝╚═════╝░╚═╝░░╚═╝╚═════╝░
%
% 230 words
%
The All Sky Automated Survey \cite[ASAS; ][]{pojmanski_all_1997, asas_2005, asas_2018} is a survey consisting of two observing stations - one in Las Campanas, Chile and the other on Maui, Hawaii. 
%
Each observatory is equipped with two CCD cameras using V and I filters and commercial f $ = 200$ mm, D $= 100$ mm lenses, although both larger (D $=250$ mm) and smaller (50-72 mm) lenses were used at earlier times.
%
The majority of the data are taken with a pixel scale of $\approx$ 15\arcsec{}.
%
ASAS splits the sky into 709 partially overlapping 9\degr{} $\times$ 9\degr{} fields, taking on average 150 3-minute exposures per night, leading to a variable cadence of 0-2 frames per night.
%
Depending on the equipment used and the mode of operation, the ASAS limiting magnitude varied between 13.5 and 15.5 mag in V, and the saturation limit was 5.5 to 7.5 mag. 
%
Precision is around 0.01-0.02 mag for bright stars and below 0.3 mag for the fainter ones. 
%
ASAS photometry is calibrated against the Tycho catalog, and its accuracy is limited to 0.05 mag for bright, non-blended stars.

@@

% 180 words

@@

%\subsection*{Dust properties from the colors in the optical} MAX 40 characters
\subsubsection*{Dust properties from optical colors}
